null_model

### 2020-07-21 analysis/ts_null_model.Rmd
save fd data for null model as csv, only include plots that meet the criteria for inclusion.
Null model in parallel.

>>>>

Calculate null models in parallel
```{r}
#number of chunks to split original dataset into 
num_groups = 4

plot_sizes <- sample_plots %>%
  count(plot_id) %>%
  arrange(desc(n)) %>%
  mutate(group = rep_len(1:num_groups, dim(.)[1]))

get_parallel_FD <- function(data, group_num){
  group_plots <- plot_sizes %>% filter(group == group_num)
  group_data <- data %>% filter(plot_id %in% group_plots$plot_id)

  future::plan(multiprocess)
  fd <- map_dfr(group_plots$plot_id[1:3], get_plot_FD, 
                   data = group_data, trait_range = 18:65, occ_df = sample_occurrence)
    #future_map(group_plots$plot_id, get_fd_safe, data = group_data)

  print(group_num)
  return(fd)
}

fd <- map_dfr(1:num_groups, get_parallel_FD, data = data)
```
